---
title: "My Excellent Research"
author: 
  - Dan Ovando
  - Daniel Ovando
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::pdf_document2:
    keep_tex: true
    includes: 
      in_header: "my-pub-header.tex"
  bookdown::html_document2: default
linkcolor: blue
always_allow_html: true
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(palmerpenguins)
library(knitr)
library(kableExtra)
library(flextable)
```

# Introduction

We found some cool stuff (Fig.\@ref(fig:main-fig))

```{r main-fig, fig.cap="Our Main Results"}

plot(1:10)
```

Here are some penguins (Table.\@ref(tab:pen-tab))

```{r pen-tab}

knitr::kable(head(penguins), caption = "Here are some penguins", 
             booktabs = FALSE, 
             longtable = FALSE, 
             format = "pipe") %>% 
  kableExtra::kable_styling(latex_options = "striped")


```



Here is a manual table, Tab.\@ref(tab:simple-table). 

\newpage

This is a manual  table (Table.\@ref(tab:simple-table))

| Thing 1 | Thing 2 | Col3 |
|---------|---------|------|
| A       | B       | C    |
| D       | E       | F    |
| G       | H       | I    |
Table:(\#tab:simple-table) Caption for a Manual Table



Here is a flipper model (Table.\@ref(tab:flipper-model))

```{r flipper-model}

mod <- lm(flipper_length_mm ~ island, data = penguins)


modelsummary::modelsummary(list("Flipper Model" = mod), stars = TRUE,
                           title = "My flipper model", 
                           output = "flextable")
```


As you can see in Equation.\@ref(eq:binom)

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

\newpage
# Supplementary Materials


\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{figure}{0}

\renewcommand{\thetable}{S\arabic{table}}

\setcounter{table}{0}

\renewcommand{\theequation}{S\arabic{equation}}

\setcounter{equation}{0}

Here are our Supplementary materials... 


Here is another flipper model (Table.\@ref(tab:si-flipper-model))

```{r si-flipper-model}

mod <- lm(flipper_length_mm ~ island + species, data = penguins)


modelsummary::modelsummary(list("SI Flipper Model" = mod), stars = TRUE,
                           title = "My SI flipper model",
                           output = "flextable")
```


As you can see in Equation.\@ref(eq:binom2)

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom2)
\end{equation} 

\newpage
```{r, child = "appendix.Rmd"}

```


