---
title: "What Makes Penguins Chonky"
author: 
  - Dan Ovando
  - Daniel Ovando
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    keep_tex: true
    includes: 
      in_header: "my-pub-header.tex"
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::html_document2: default
linkcolor: blue
always_allow_html: true
params:
  results_name: ["v1.0"]
bibliography: pubs-in-rmarkdown.bib
csl: fish-and-fisheries.csl
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(palmerpenguins)
library(knitr)
library(kableExtra)
library(flextable)
library(here)

results_name <- params$results_name

results_path <- here("results", results_name)

# load results

load(file.path(results_path, "penguin-plots.Rdata"))

load(file.path(results_path, "penguin-models.Rdata"))


```

# Introduction

Penguins are pretty great. Sort of, some people find them scary. However, @keum2001 showed that both fat and imaginary penguins can "decay amplitudes in perturbative QCD picture". Since that sounds pretty bad, we should probably figure out what makes penguins fat, if not imaginary. The mean penguin weighs `r mean(penguins$body_mass_g, na.rm = TRUE) / 1000 * 2.204623` pounds. 

Male penguins tend to be fatter than female penguins, and it looks like Gentoo penguins on Biscoe island might be at serious risk of perturbing the QCD picture (Fig.\@ref(fig:weight-fig)) [@horst2020;@keum2001]. 

```{r weight-fig, fig.cap="Distribution of penguin weight in grams by sex,species, and island."}

weight_plot
```

But, it seems like bill length and flipper length matter too (Fig.\@ref(fig:weight-plot-2)). 

```{r weight-plot-2, fig.cap = "Penguin body mass from @horst2020 as a function of bill length and flipper length"}
weight_things_plot
```

For those that like tables, here's a table of some penguins (Table.\@ref(tab:pen-tab)). 

```{r pen-tab}

knitr::kable(head(penguins), caption = "Here are some penguins", 
             booktabs = FALSE, 
             longtable = FALSE, 
             format = "pipe") %>% 
  kableExtra::kable_styling(latex_options = "striped")


```


# Methods

Here are two models we tried (Tab.\@ref(tab:simple-table)). 


| Model   | Abrev.  | Description |
|---------|---------|------|
| First   | A       | Islands!  |
| Second  | B      | Flippers!  |
Table:(\#tab:simple-table) Candidate models

\newpage
# Results

Here are our models (Table.\@ref(tab:flipper-model))

```{r flipper-model}


modelsummary::modelsummary(list("A" = model_a,
                                "B" = model_b), stars = TRUE,
                           title = "Why are penguins fat?")
```

# Discussion

Looks like team flipper is a better model than team island.

For future research, we might try and model some presence and absence data using the binomial function \@ref(eq:binom)

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

If someone gives us a lot more funding we will also do some state-space modeling [@brooks2017], or some Bayesian stuff [@mcelreath2020]. 

# References
<div id="refs"></div>


\newpage
# Supplementary Materials


\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{figure}{0}

\renewcommand{\thetable}{S\arabic{table}}

\setcounter{table}{0}

\renewcommand{\theequation}{S\arabic{equation}}

\setcounter{equation}{0}

Here are our Supplementary Materials


Here is another flipper model (Table.\@ref(tab:si-flipper-model))

```{r si-flipper-model}

mod <- lm(flipper_length_mm ~ island + species + sex, data = penguins)


modelsummary::modelsummary(list("SI Flipper Model" = mod), stars = TRUE,
                           title = "My SI flipper model")
```


As a reminder, we thought about an equation \@ref(eq:binom2). 

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom2)
\end{equation} 

\newpage
```{r, child = "appendix.Rmd"}

```

