---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(bookdown)
library(xaringan)
library(ggplot2)
library(dplyr)
library(tidyr)
library(citr)
library(rticles)

```


# Publications with R Markdown

<!-- badges: start -->
<!-- badges: end -->

This repository is equipped with `renv`

1. Make sure you have some sort of LaTeX distribution installed on your computer. If you've ever successfully Knit an R Markdown document to PDF, you should be fine. If you're not sure, I recommend using [`tinytex`](https://yihui.name/tinytex/). 

```
install.packages('tinytex')
tinytex::install_tinytex()
```

2. Fork the clone to your machine, or just download the repo. 

3. Open R and set your working directory of the cloned repository (or just use RStudio projects)

4. This project is set up with [`renv`](https://rstudio.github.io/renv/articles/renv.html) to manage package dependencies. Inside R (and with your working directory set correctly) run `renv::restore()`. E.g. if you stored this repo in `"/Users/danovan/projects/publications-with-rmarkdown"`, when you type `getwd` in the R console you should see `"/Users/danovan/projects/publications-with-rmarkdown"`. You will run into some odd problems if your working directory is set to say `"/Users/place-where-every-project-lives` and this project is just a folder somewhere in that mess. 

Follow all prompts that come up after running `renv::restore()`. This will install the correct versions of all the packages needed to replicate our results. Packages are installed in a stand-alone project library for this project, and will not affect your installed R packages anywhere else. 

The preview version of RStudio has some neat [features for R Markdown](https://rstudio.com/products/rstudio/download/preview/). If you'd like to install it you can do so [here](https://rstudio.com/products/rstudio/download/preview/) but it's not needed. 

# R Markdown for Publications

A short presentation for Eco-Data-Science discussing solutions to some specific issues with using R Markdown for scientific publication. 

There are countless great R Markdown materials out there, e.g. [Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/). However, weird as it may seem, we in academia are not the primary user for R Markdown! I've found as a result that almost all of the materials out there are geared towards more industry / informal sharing of documents. There aren't a lot of resources dealing with all the specific issues though of getting your work into the arcane requirements of the Academic Journal of Scientific Seriousness. 

The goal of this talk is to walk you through how to use R Markdown for the specific task of academic publications. 


***This is not an intro to R Markdown: I will assume that you know how to do the basics in R Markdown***

1. Why R Markdown for Scientific Publications (and dissertations/theses!)

2. A quick discussion of [`rticles`](https://github.com/rstudio/rticles)

3. Formatting References

4. Cross-referencing
    - Figures, tables, equations, sections

5. Workflow
    - Updating results
    - Collaborating! i.e. what to do without track changes

6. If time permits, a quick tour of the [`gauchodown`](https://github.com/DanOvando/gauchodown) template for UCSB dissertations/theses
